The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
update table 3

\begin{table}
  \caption{Number of benchmarks used in the \maintrack (by division)}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ABVFP      &     -- &     -- &      1 &     1 \\
    ALIA       &     42 &     42 &     42 &    42 \\
    AUFBVDTLIA &     -- &     -- &   1709 &  1709 \\
    AUFDTLIA   &     -- &     -- &    728 &   728 \\
    AUFLIA     &      4 &      4 &      4 &     4 \\
    AUFLIRA    &  19849 &  19849 &  20011 & 20011 \\
    AUFNIRA    &   1050 &   1050 &   1480 &  1480 \\
    BV         &     85 &     85 &   5151 &  5751 \\
    BVFP       &     -- &     -- &     24 &    24 \\
    FP         &     -- &     -- &     61 &    61 \\
    LIA        &    201 &    201 &    388 &   388 \\
    LRA        &    339 &    339 &   2419 &  2419 \\
    NIA        &      9 &      9 &     14 &    14 \\
    NRA        &   3788 &   3788 &   3811 &  3813 \\
    QF\_ABV    &  14720 &  14720 &  15061 & 15066 \\
    QF\_ABVFP  &     -- &     -- &  18129 & 18129 \\
    QF\_ALIA   &    134 &    139 &    139 &   139 \\
    QF\_ANIA   &      6 &      8 &      8 &     8 \\
    QF\_AUFBV  &     37 &     37 &     31 &    31 \\
    QF\_AUFLIA &   1009 &   1009 &   1009 &  1009 \\
    QF\_AUFNIA &     21 &     21 &     17 &    17 \\
    QF\_AX     &    551 &    551 &    551 &   551 \\
    QF\_BV     &  26414 &  26414 &  40043 & 40102 \\
    QF\_BVFP   &      7 &      7 &  17215 & 17215 \\
    QF\_DT     &     -- &     -- &   8000 &  8000 \\
    QF\_FP     &  34413 &  34413 &  40302 & 40300 \\
    QF\_IDL    &   2094 &   2094 &   2193 &  2193 \\
    QF\_LIA    &   5839 &   5839 &   6141 &  6947 \\
    QF\_LIRA   &      6 &      6 &      7 &     7 \\
    QF\_LRA    &   1626 &   1626 &   1649 &  1649 \\
    QF\_NIA    &   8475 &   8593 &  23876 & 23876 \\
    QF\_NIRA   &      2 &      2 &      3 &     3 \\
    QF\_NRA    &  10184 &  10245 &  11354 & 11489 \\
    QF\_RDL    &    220 &    220 &    255 &   255 \\
    QF\_SLIA   &     -- &     -- &     -- & 72705 \\
    QF\_UF     &   6649 &   6649 &   6650 &  7423 \\
    QF\_UFBV   &     31 &     31 &     31 &  1224 \\
    QF\_UFIDL  &    441 &    441 &    428 &   428 \\
    QF\_UFLIA  &    598 &    598 &    583 &   583 \\
    QF\_UFLRA  &   1627 &   1627 &   1284 &  1284 \\
    QF\_UFNIA  &      7 &      7 &      7 &     7 \\
    QF\_UFNRA  &     34 &     34 &     36 &    36 \\
    UF         &   2839 &   2839 &   7562 &  7562 \\
    UFBV       &     71 &     71 &    200 &   200 \\
    UFDT       &     -- &     -- &   4535 &  4527 \\
    UFDTLIA    &     -- &     -- &    303 &   303 \\
    UFIDL      &     68 &     68 &     68 &    68 \\
    UFLIA      &   8404 &   8404 &  10137 & 10137 \\
    UFLRA      &     25 &     25 &     15 &    15 \\
    UFNIA      &   2319 &   2319 &   3308 &  3308 \\
    \midrule
    Total      & 154238 & 154424 & 256973 & 333241 \\
    \bottomrule
  \end{tabular}}
\end{table}

>>>>

\begin{table}
  \caption{Number of benchmarks used in the \maintrack (by division). Numbers in brackets indicate the (rounded) percentage of problems with different statuses, which are (sat,unsat) in 2015/6 and (sat,unsat,unknown) in 2017/8.}
  \label{table:benchmarks-main-track}
  \centering
  \scalebox{.9}[.8]{\begin{tabular}{lrrrr}
    \toprule
    Division & \multicolumn{1}{c}{2015} & \multicolumn{1}{c}{2016} & \multicolumn{1}{c}{2017} & \multicolumn{1}{c}{2018} \\
    \midrule
    ABVFP & - & - & - & 1 (0:0:100)\\
ALIA & 42 (2:98) & 42 (2:98) & 42 (2:98:0) & 42 (2:98:0)\\
AUFBVDTLIA & - & - & 1709 (0:1:98) & 1709 (0:1:98)\\
AUFDTLIA & - & - & 728 (0:0:100) & 728 (0:0:100)\\
AUFLIA & 4 (25:75) & 4 (25:75) & 4 (25:75:0) & 4 (25:75:0)\\
AUFLIRA & 19849 (1:99) & 19849 (1:99) & 20011 (0:99:1) & 20011 (0:99:1)\\
AUFNIRA & 1050 (0:100) & 1050 (0:100) & 1480 (0:71:29) & 1480 (0:71:29)\\
BV & 85 (34:66) & 85 (34:66) & 5151 (2:2:97) & 5751 (10:86:4)\\
BVFP & - & - & - & 24 (0:0:100)\\
FP & - & - & - & 61 (0:0:100)\\
LIA & 201 (5:95) & 201 (5:95) & 388 (38:60:2) & 388 (38:60:2)\\
LRA & 339 (6:94) & 339 (6:94) & 2419 (17:46:38) & 2419 (29:64:8)\\
NIA & 9 (67:33) & 9 (67:33) & 14 (43:29:29) & 14 (43:29:29)\\
NRA & 3788 (0:100) & 3788 (0:100) & 3811 (0:100:0) & 3813 (0:100:0)\\
QF\_ABV & 14720 (68:32) & 14720 (68:32) & 15061 (69:31:0) & 15066 (69:31:0)\\
QF\_ABVFP & - & - & - & 18129 (78:22:1)\\
QF\_ALIA & 134 (40:60) & 139 (42:58) & 139 (42:58:0) & 139 (42:58:0)\\
QF\_ANIA & 6 (0:100) & 8 (0:100) & 8 (0:100:0) & 8 (0:100:0)\\
QF\_AUFBV & 37 (16:84) & 37 (16:84) & 31 (19:81:0) & 31 (19:81:0)\\
QF\_AUFLIA & 1009 (49:51) & 1009 (49:51) & 1009 (49:51:0) & 1009 (49:51:0)\\
QF\_AUFNIA & 21 (29:71) & 21 (29:71) & 17 (29:71:0) & 17 (29:71:0)\\
QF\_AX & 551 (49:51) & 551 (49:51) & 551 (49:51:0) & 551 (49:51:0)\\
QF\_BV & 26414 (35:65) & 26414 (35:65) & 40043 (32:59:8) & 40102 (36:64:0)\\
QF\_BVFP & 7 (14:86) & 7 (14:86) & 17215 (81:18:0) & 17215 (81:18:0)\\
QF\_DT & - & - & 8000 (0:0:100) & 8000 (45:55:0)\\
QF\_FP & 34413 (50:50) & 34413 (50:50) & 40302 (50:50:1) & 40300 (50:50:1)\\
QF\_IDL & 2094 (61:39) & 2094 (61:39) & 2193 (58:37:5) & 2193 (58:37:4)\\
QF\_LIA & 5839 (51:49) & 5839 (51:49) & 6141 (52:46:2) & 6947 (55:43:1)\\
QF\_LIRA & 6 (17:83) & 6 (17:83) & 7 (14:71:14) & 7 (14:71:14)\\
QF\_LRA & 1626 (61:39) & 1626 (61:39) & 1649 (57:41:2) & 1649 (57:41:1)\\
QF\_NIA & 8475 (98:2) & 8593 (96:4) & 23876 (59:13:28) & 23876 (59:20:20)\\
QF\_NIRA & 2 (0:100) & 2 (0:100) & 3 (0:67:33) & 3 (0:67:33)\\
QF\_NRA & 10184 (52:48) & 10245 (52:48) & 11354 (44:47:10) & 11489 (44:47:9)\\
QF\_RDL & 220 (49:51) & 220 (49:51) & 255 (43:44:13) & 255 (43:44:13)\\
QF\_SLIA & - & - & - & 72705 (0:0:100)\\
QF\_UF & 6649 (38:62) & 6649 (38:62) & 6650 (38:62:0) & 7423 (42:58:0)\\
QF\_UFBV & 31 (0:100) & 31 (0:100) & 31 (0:100:0) & 1224 (53:47:0)\\
QF\_UFIDL & 441 (24:76) & 441 (24:76) & 428 (25:75:0) & 428 (25:75:0)\\
QF\_UFLIA & 598 (67:33) & 598 (67:33) & 583 (69:31:0) & 583 (69:31:0)\\
QF\_UFLRA & 1627 (48:52) & 1627 (48:52) & 1284 (60:40:0) & 1284 (60:40:0)\\
QF\_UFNIA & 7 (0:100) & 7 (0:100) & 7 (0:100:0) & 7 (0:100:0)\\
QF\_UFNRA & 34 (47:53) & 34 (47:53) & 36 (58:31:11) & 36 (58:31:11)\\
UF & 2839 (28:72) & 2839 (28:72) & 7562 (10:44:46) & 7562 (10:46:44)\\
UFBV & 71 (25:75) & 71 (25:75) & 200 (34:48:17) & 200 (34:48:17)\\
UFDT & - & - & 4535 (0:9:90) & 4527 (1:41:58)\\
UFDTLIA & - & - & 303 (0:0:100) & 303 (0:0:100)\\
UFIDL & 68 (9:91) & 68 (9:91) & 68 (4:84:12) & 68 (4:84:12)\\
UFLIA & 8404 (0:100) & 8404 (0:100) & 10137 (0:76:24) & 10137 (0:76:23)\\
UFLRA & 25 (20:80) & 25 (20:80) & 15 (33:67:0) & 15 (33:67:0)\\
UFNIA & 2319 (0:100) & 2319 (0:100) & 3308 (0:74:26) & 3308 (0:74:26)\\
\iffalse
 ABVFP & - & - & - & 1 (0:0)\\
ALIA & 42 (2:98) & 42 (2:98) & 42 (2:98) & 42 (2:98)\\
AUFBVDTLIA & - & - & 1709 (0:1) & 1709 (0:1)\\
AUFDTLIA & - & - & 728 (0:0) & 728 (0:0)\\
AUFLIA & 4 (25:75) & 4 (25:75) & 4 (25:75) & 4 (25:75)\\
AUFLIRA & 19849 (1:99) & 19849 (1:99) & 20011 (0:99) & 20011 (0:99)\\
AUFNIRA & 1050 (0:100) & 1050 (0:100) & 1480 (0:71) & 1480 (0:71)\\
BV & 85 (34:66) & 85 (34:66) & 5151 (2:2) & 5751 (10:86)\\
BVFP & - & - & - & 24 (0:0)\\
FP & - & - & - & 61 (0:0)\\
LIA & 201 (5:95) & 201 (5:95) & 388 (38:60) & 388 (38:60)\\
LRA & 339 (6:94) & 339 (6:94) & 2419 (17:46) & 2419 (29:64)\\
NIA & 9 (67:33) & 9 (67:33) & 14 (43:29) & 14 (43:29)\\
NRA & 3788 (0:100) & 3788 (0:100) & 3811 (0:100) & 3813 (0:100)\\
QF\_ABV & 14720 (68:32) & 14720 (68:32) & 15061 (69:31) & 15066 (69:31)\\
QF\_ABVFP & - & - & - & 18129 (78:22)\\
QF\_ALIA & 134 (40:60) & 139 (42:58) & 139 (42:58) & 139 (42:58)\\
QF\_ANIA & 6 (0:100) & 8 (0:100) & 8 (0:100) & 8 (0:100)\\
QF\_AUFBV & 37 (16:84) & 37 (16:84) & 31 (19:81) & 31 (19:81)\\
QF\_AUFLIA & 1009 (49:51) & 1009 (49:51) & 1009 (49:51) & 1009 (49:51)\\
QF\_AUFNIA & 21 (29:71) & 21 (29:71) & 17 (29:71) & 17 (29:71)\\
QF\_AX & 551 (49:51) & 551 (49:51) & 551 (49:51) & 551 (49:51)\\
QF\_BV & 26414 (35:65) & 26414 (35:65) & 40043 (32:59) & 40102 (36:64)\\
QF\_BVFP & 7 (14:86) & 7 (14:86) & 17215 (81:18) & 17215 (81:18)\\
QF\_DT & - & - & 8000 (0:0) & 8000 (45:55)\\
QF\_FP & 34413 (50:50) & 34413 (50:50) & 40302 (50:50) & 40300 (50:50)\\
QF\_IDL & 2094 (61:39) & 2094 (61:39) & 2193 (58:37) & 2193 (58:37)\\
QF\_LIA & 5839 (51:49) & 5839 (51:49) & 6141 (52:46) & 6947 (55:43)\\
QF\_LIRA & 6 (17:83) & 6 (17:83) & 7 (14:71) & 7 (14:71)\\
QF\_LRA & 1626 (61:39) & 1626 (61:39) & 1649 (57:41) & 1649 (57:41)\\
QF\_NIA & 8475 (98:2) & 8593 (96:4) & 23876 (59:13) & 23876 (59:20)\\
QF\_NIRA & 2 (0:100) & 2 (0:100) & 3 (0:67) & 3 (0:67)\\
QF\_NRA & 10184 (52:48) & 10245 (52:48) & 11354 (44:47) & 11489 (44:47)\\
QF\_RDL & 220 (49:51) & 220 (49:51) & 255 (43:44) & 255 (43:44)\\
QF\_SLIA & - & - & - & 72705 (0:0)\\
QF\_UF & 6649 (38:62) & 6649 (38:62) & 6650 (38:62) & 7423 (42:58)\\
QF\_UFBV & 31 (0:100) & 31 (0:100) & 31 (0:100) & 1224 (53:47)\\
QF\_UFIDL & 441 (24:76) & 441 (24:76) & 428 (25:75) & 428 (25:75)\\
QF\_UFLIA & 598 (67:33) & 598 (67:33) & 583 (69:31) & 583 (69:31)\\
QF\_UFLRA & 1627 (48:52) & 1627 (48:52) & 1284 (60:40) & 1284 (60:40)\\
QF\_UFNIA & 7 (0:100) & 7 (0:100) & 7 (0:100) & 7 (0:100)\\
QF\_UFNRA & 34 (47:53) & 34 (47:53) & 36 (58:31) & 36 (58:31)\\
UF & 2839 (28:72) & 2839 (28:72) & 7562 (10:44) & 7562 (10:46)\\
UFBV & 71 (25:75) & 71 (25:75) & 200 (34:48) & 200 (34:48)\\
UFDT & - & - & 4535 (0:9) & 4527 (1:41)\\
UFDTLIA & - & - & 303 (0:0) & 303 (0:0)\\
UFIDL & 68 (9:91) & 68 (9:91) & 68 (4:84) & 68 (4:84)\\
UFLIA & 8404 (0:100) & 8404 (0:100) & 10137 (0:76) & 10137 (0:76)\\
UFLRA & 25 (20:80) & 25 (20:80) & 15 (33:67) & 15 (33:67)\\
UFNIA & 2319 (0:100) & 2319 (0:100) & 3308 (0:74) & 3308 (0:74)\\
\fi
    \midrule
    Total      & 154238 (40:60) & 154424 (40:60) & 256973 (37:46:17) & 333241 (33:39:28)\\
    \bottomrule
  \end{tabular}}
\end{table}
